Reviewer comments from PeerJ

### 2015-03-06 PeerJResponse.tex
Edits
Edits to response concerning phasing of SNPs

\res{We have addressed the comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products was never performed as primer combinations for each of the 2 PCRs gave us the expected sized bands. Primers were designed off of previously sequenced teosinte and maize sequences \lev{these were from John Doebley, do we need to say this? I don' think they were published ever} and were initially tested in both maize and teosinte for validity.  We have clarified this point in text \lev{text, line numbers here} as well added additional labelling to the gel image (Figure 2 \lev{check to make sure figure number doesn't change during edits})}.

@@

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\
\lev{this will be too much. I can label the brightest band (1kb) and the top and bottom bands}
\mbh{I'd label as many as it takes so that it's obvious what intervening band sizes are.  We'll want to define the abbreviations too}
\lev{usually the bottom, middle brightest and top are labelled so I will do that}

@@

\lev{Maybe in the text I can clarify total bands for individuals. I.e. if an individual is Hop/Hop, it will have a total of two bands that are split between the two PCRs, whereas if you are a heterozygote you will have 3 split between two PCRs. I wonder if we should ditch this figure entirely and I can draw up a cartoon one?}
\mbh{since reviewer 2 is also concerned about the PCR and this is the only thing the editor really mentioned, I think we need to be pretty thorough here.  Ideally we would have a Hop/Hop homozygote, a Hop/No Hop heterozygote, and a No Hop/No Hop homozygote in the figure.  We don't need the Pif since this really isn't mentioned in the manuscript.  Do you have gel figures showing both homozygotes and the heterozygote banding patterns? I'm afraid a cartoon would send the message that we don't have clear PCR results}
\jri{agree with the huff}
\lev{I do not have gel figures. I am guessing the ones that had been saved online in Jeff's lab have been tossed. I can check my lab notebook and see if there is something to scan, otherwise there will not be a figure with all of those genotypes that we can give to them.}

@@

\lev{yes SNPs within 5KB window are a haplotype. I don't know about the diploid/phasing stuff. Yes to maize assignment. Point of figure is that low assignment to maize in populations with high frequency of Hopscotch. Am plotting the assigment value across a region of chromosome 1. I showed a region and not entire chromosome to be able to highlight the position of tb1 and so that you can see the difference in assignment values.}

\mbh{methods say that you used phased data from Tanja's manuscript.  Did she give you phased data or did you phase this yourself with fastPHASE?  Either way, probably best to mention the data were phased with fastPHASE and add a citation to the methods paper for this}

\lev{I believe that she phased it since it was the exact thing that she used for her BayEnv stuff}

\res{Data were previously phased using fastPHASE (\lef{cite tanja and fastPHASE paper}). We have added clarifying statements to the text of this section, pages X, lines X-X. Figure 4 is showing maize population assignment for adjacent 5 kb windows. The STRUCTURE analysis was performed for the entirety of chromosome 1; however, the figure only shows a zoomed in portion to highlight the section of chromosome 1 that contains the \emph{tb1} region. The results in Table 4 reflect the entire chromosome.}

>>>>

\res{We have addressed the comments from Reviewer 2 regarding the validity of the PCR assays. Sequencing of PCR products was never performed as primer combinations for each of the 2 PCRs gave us the expected sized bands. Primers were designed off of previously sequenced teosinte and maize sequences provided by John Doebley, and were initially tested in both maize and teosinte for validity.  We have clarified this point in text \lev{text, line numbers here} as well added additional labelling to the gel image (Figure 2).}

@@

5) Fig. S2. Annotate this figure to show the size (bp) of each band in the 1 kb ladder. The caption should also define the abbreviations used in the labels. \\

\res{We have edited this figure to be more clear.}

@@

\res{We have edited Fig. S2 to be more clear and include appropriate labels and explanations.}

@@

\res{Data were previously phased using fastPHASE (\citet{Pyhajarvi2013, Scheet2006}). We have added clarifying statements to the text of this section, pages 5, lines 104-105. Figure 4 is showing maize population assignment for adjacent 5 kb windows. The STRUCTURE analysis was performed for the entirety of chromosome 1; however, the figure only shows a zoomed in portion to highlight the section of chromosome 1 that contains the \emph{tb1} region. The results in Table 4 reflect the entire chromosome.}
